While scalability is the major benefit of local Lagrangian flow maps, this benefit comes with certain limitations as shown in our evaluation.
%
First, as observed for the Jet data set, a vector field with very high velocity might be poorly reconstructed.
%
%In particular, we observe this for the Jet data set.
%
Second, Lagrangian$_{Local}$ reconstruction accuracy can be adversely affected if the storage interval is too large or if too few samples are stored.
%
This limits the potential amount of data reduction in comparison to Lagrangian$_{Dist}$.
%
%is effective for several practical configurations, the accuracy suffers when a large percentage of particles 
%is less accurate than Lagrangian$_{Dist}$ when the storage interval is large or the number of particles used to sample the domain is small, i.e., it limits the degree of data reduction.
%
%Prior works have demonstrated that Lagrangian$_{Dist}$ can provide high accuracy while using a small number of samples. 
%, i.e., providing a significant data reduction (for example, 1:64 data reduction factor corresponds to a $>$98\% compression of time-varying vector data).
%
%The Lagrangian$_{Local}$ strategy leverages this knowledge and discards particle trajectories in order to remain communication-free.
%
%However, this strategy is only effective as long as Lagrangian$_{Local}$ still stores a sufficient number of samples. 
%
While both Lagrangian$_{Dist}$ and Lagrangian$_{Local}$ show error (as shown in Figure~\ref{fig:strongscaling}), the error of Lagrangian$_{Local}$ increases faster when using a small number of samples or large storage intervals.
%

We briefly discuss two solutions to these challenges.
%
The first potential solution is to detect high velocity regions, and adapt execution to adopt some local communication with spatially adjacent ranks.
%
%Infrequent global communication would then also be required to exchange particles before storing to disk.
%Such a technique can be triggered if high velocity regions are detected.
%For example, the Los Alamos National Laboratory MPAS-O uses an integrated online Lagrangian analysis system that uses a combination of frequent local communication and infrequent global communication to perform particle exchange operations~\cite{VANSEBILLE201849}.
%
%However, we are unaware of technical details or a study of this system and expect its performance would be dependent on the specific application (underlying vector field), domain decomposition, rank placement, and synchronization.
%
The second solution is to stop discarding trajectories that hit the domain boundary, and instead utilize them for reconstruction. 
%
In this case, Lagrangian analysis could remain communication-free but would need enhancements not only for how to represent trajectories (termination location and time, number of points stored along pathline), but also would require a novel post hoc interpolation scheme.
%
For example, a recent work on post hoc reconstruction leveraged deep learning to upsample 2D FTLE fields derived from reduced Lagrangian flow maps~\cite{jakob2020fluid}.
%
%In this case, Lagrangian analysis would remain communication-free but would need enhancements not only for how to represent trajectories that end abruptly (location, time, number of points along the curve, etc.) involves Lagrangian analysis remaining communication-free while adopting a more complex strategy for domain coverage with particle termination information (location, time) stored.
%
%A flow map with arbitrary termination times for particle trajectories, however, would require a novel post hoc interpolation scheme.
%
We believe these challenges should be pursued for future work. 
%
That said, we believe a significant number of use cases for Lagrangian analysis in practice today would not encounter these limitations. 
% aforementioned limitations can be addressed via these solutions.


THe flow maps we use showed that over a single interval - reconstruction was good. when interpolation several, error propagated. Thus, future work focusing on time-varying visualizations would be nice. 

Further, future work that can help adaptively decide time intervals would be valuable given currently there is no way to make these decisions beforehand. 
